\section{Lessons learned}

We had two major challenges during execution of the project


\begin{enumerate}

\item When we started with the project the problem was not well understood by the team. Our work on initial designs and flaws in our solutions made us think more about the problem and what we are trying to solve. As we are building a new system, we started listing down system properties or requirements our system has to satisfy. This gave the basis for evaluating designs. We thank professor Julia and everyone in ReSeSS lab for helping us on this.

\item Our initial problem only contained end-users as stakeholders and solutions directed towards that. Later, we realized for a developer ensuring system properties such fairness and deterministic behaviour of the system is also an important part of our problem. We learned that when designing a new system we need to map all stakeholders first and list their varying interests in the system.

\item We spent a considerable amount of time in achieving right architecture for the system like working on kernel modules which can be avoided and rough prototype would have proved the same point.
\end{enumerate}


\section{Next steps}

\begin{enumerate}

\item Currently the only constant cost is used for system calls, this should be replaced by cost models for variable cost system calls.
\item Evaluate amount of energy consumed by the framework.
\item Instrument and Evaluate functioning of the framework on open source mobile applications.
\item A user study for evaluation of Usability of the framework. 

\end{enumerate}

\section{contribution of each team member}

\subsection{Harsha}

\begin{enumerate}
\item Design of the solution 
\item Architecture of implementation
\item Implementation of Account manager
\end{enumerate}

\subsection{Satish}
\begin{enumerate}
\item Design of the solution
\item System call interceptor
\item ECA App and Evaluation
\end{enumerate}


